Test Suite Parallelization in Open-Source Projects: A Study on Its Usage and Impact

### 2019-05-21 OLD/journal/paper.tex
moving dirs

\usepackage{graphicx}
% *** CITATION PACKAGES ***
%
\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  \usepackage[nocompress]{cite}
\else
  % normal IEEE
  \usepackage{cite}
\fi

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi

@@

\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{balance}
\usepackage{float}
\usepackage{url}
\usepackage{tabularx}
\usepackage[table]{xcolor}
\usepackage{booktabs}
\usepackage{amsmath} 
\usepackage{subfigure} 
\usepackage{multirow}
\usepackage{mdframed}
\usepackage{xcolor}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\title{Test Suite Parallelization in Open-Source Projects:\\ A Study on Its Usage and Impact}

\author{Sotero Junior, Jeanderson Candido, Marcio Ribeiro
        and~Marcelo d'Amorim

% <-this % stops a space
\IEEEcompsocitemizethanks{
\IEEEcompsocthanksitem 
S. Junior and M. d'Amorim are with the Informatics Center, Federal Univer- sity of Pernambuco, Recife, PE 50732-970, Brazil.

E-mail: \{srsj2, damorim\}@cin.ufpe.br

\IEEEcompsocthanksitem 
M. Ribeiro was with the Computing Institute, Federal University of Alagoas, Maceio, AL 57072-900, Brazil.

E-mail: marcio@ic.ufal.br
}% <-this % stops an unwanted space
\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~45, No.~6, June~2019}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}

@@

Considering a set of \numSubjs{} popular Java projects we analyzed, we
found that \percentMedLongRunning{} of the projects contain costly
test suites but parallelization features still seem underutilized in
practice~---~only \percentParallelUpdated{} of costly projects use
parallelization.  The main reported reason for adoption resistance was
the concern to deal with concurrency issues.  Results suggest that, on
average, developers prefer high predictability than high performance
in running tests.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
test suite, parallelization, Maven, Java, Software Engineering.
\end{IEEEkeywords}}

% make the title area
\maketitle
\IEEEdisplaynontitleabstractindextext
\IEEEpeerreviewmaketitle

\IEEEraisesectionheading{
\section{Introduction}
\label{sec:introduction}}

\input{intro}

%\hfill lorem ipsum

%\hfill August 26, 2015

% SECTION 2
\section{Parallel Execution of Test Suites}
Figure~\ref{fig:levels} illustrates different levels where
parallelism in test execution can be obtained.
The highest level indicates
parallelism obtained through different machines on the
network.  For instance, using virtual machines from a cloud service to
\begin{wrapfigure}{r}{0.13\textwidth}  
  \vspace{-2mm}
  \centering
  %  \includegraphics[width=0.35\textwidth]{figs/parallel-levels.pdf}    
  \includegraphics[width=2cm]{figs/parallel-levels-short.pdf}  
  \caption{\label{fig:levels}Levels of parallelism.}
  \vspace{-2mm}
\end{wrapfigure}

distribute test execution.  The lowest levels denote parallelism
obtained within a single machine.  These levels are complementary:
the lowest levels leverage the computing power of server
nodes whereas the highest level leverages the aggregate processing
power of a network of machines.
This paper focuses on low-level parallelism, where computation can be
offloaded at different CPUs within a machine and at different threads
within each CPU.  This form of parallelism is enabled through build
systems (spawning processes in different CPUs) and testing frameworks
(spawning threads in one given CPU).  It is important to note that a variety
of testing frameworks provide today support for parallel test
execution (e.g., JUnit~\cite{junit-org}, TestNG~\cite{testng}, and
NUnit~\cite{nunit}) as to benefit from the available power of popular multi-core processors.
In the following, we elaborate relevant features of testing frameworks
and build systems for parallelization.  We focused on Java, Maven, and JUnit but the
discussion can be generalized to other language and tools.

@@

% SECTION 3

@@

We used \github{}'s search API~\cite{githubsearch} to identify
projects that satisfy the following criteria: (1) the primary language
is Java\footnote{In case of projects in multiple languages, the
  \github{} API considers the predominant language as the primary
  language.}, (2) the project has at least 100 stars, (3) the latest
update was on or after January 1st, 2016, and (4) the \emph{readme}
file contains the string \emph{mvn}.  We focused on Java for its
popularity.  Although there is no clearcut limit on the number of
\github{} stars~\cite{github-stars} to define relevant projects, we
observed that one hundred stars was enough to eliminate trivial subjects. The
third
criteria serves to skip projects without recent activity. The fourth
criteria is an approximation to find Maven projects.\Comment{ The
  rationale is that if the string \emph{mvn} exists in the
  \emph{readme} file, it may represent a Maven call (\eg, to compile
or to test the project).} We focused on Maven for its popularity on
Java projects.  Important to highlight that, as of now, the
\github{}'s search API can only reflect contents from repository
statistics (\eg, number of forks, main programming language); it does
not provide a feature to search for projects containing certain files
(\eg{}, \emph{pom.xml}) in the directory structure. 
\textcolor{red}{[S.J: Hoje em dia ja e possivel buscar projeto que contenha determinado arquivo pelo Github API (ex.: pom.xml), SearchCode, foi utilizado PyGithub para filtrar os projetos ]}

Figure~\ref{fig:subject-query} illustrates the query to the \github{}
API as an HTTP request.   The result set is sorted
in descending order of stars.

\begin{figure}[t!]
\centering
\tiny
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    showstringspaces=false
}
\begin{lstlisting}
https://api.github.com/search/repositories?q=language:java
 +stars:>=100+pushed:>=2016+mvn%20in:readme&sort=stars
\end{lstlisting}
  \vspace{-3mm}
  \caption{\label{fig:subject-query} Query to the \github{} API for
  projects that (1) use Java, (2) contains at least 100
  stars, (3) has been updated on January 1st, 2016 (or later), (4) contains
  the string \emph{mvn} in the \emph{readme} file.}
  \vspace{-3mm}
\end{figure}

We used the following methodology to select projects for analysis. After obtaining the list of potential projects from GitHub, we
filtered those
containing a \pomf{} file in the root directory.\Comment{  A Maven project may
contain several sub-modules with multiple \pomf{} files.}
Then, considering this set of Maven projects, we
executed the tests for \SubjectsReruns{} times to discard those projects with
issues
in the build file and non-deterministic results observed from sequential
executions.
As of August 25th 2017, our search criteria returned a total of
\SubjectsGithub{}
subjects.
From this set of projects,
\SubjectsGithubNotMaven{} projects were not Maven or did not have a
\pomf{} in the root directory, 
\SubjectsGithubNotTestable{} projects were not considered because of
environment incompatibility
(\eg, missing\Comment{ required web browser or database management
system}~DBMS),
\SubjectsGithubFlaky{} projects were discarded because of
``flaky tests''~\cite{luo-etal-fse2014}. A ``flaky'' test is a test that passes
or fails under
the same circumstances leading to non-deterministic results.
As some of our experiments consist of running tests on different
threads, we ignored these projects as it would be impractical
to identify whether a test failed due to a race condition or some
other source of flakiness.
From the remaining \SubjectsGithubConsistant{} projects with
deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
projects with \SuiteFailingThreshold{} or more failing tests as to
reduce bias. For the
remaining projects with failing tests, we used the JUnit's
\CodeIn{@Ignore} annotation to ignore failing tests.
Our final set of subjects contains \numSubjs{} projects. 
 \textcolor{red}{[S.J: Utilizando o script desse experimento, Foram encontrado um total de 4111, onde 3154 nao eram Maven e 957 eram Maven. Dos 3154 que nao eram Maven, 2302 eram Gradle (73\%) ]}

 Figure~\ref{fig:subjects} summarizes our sample set.

\begin{figure}[ht]
  \vspace{-5mm}
  \centering
  \includegraphics[width=0.27\textwidth]{results/piechart-subjs.pdf}
  \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
  hosted on \github{}. From this initial sample, we ignored
  \SubjectsGithubNotMaven{} projects without Maven support,
  \SubjectsGithubNotTestable{} with missing dependencies,
  \SubjectsGithubFlaky{} projects with flaky tests, and
  \SubjectsGithubTooManyFailures{} projects had at least
  \SuiteFailingThreshold{} of failing tests. We considered
  \numSubjs{} projects to conduct our study.}
\end{figure}

\label{sec:setup}

To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel processor
machine with eight virtual CPUs (four cores with two native threads each) and
16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr (64-bit version).  We
used\Comment{ Git,} Java 8 and Maven 3.3.9 to build projects and run test
suites. To process test results and generate plots we used Python\Comment{ 3.4},
Bash, R and Ruby\Comment{ 2.3}.  All source artifacts are publicly available for
replication on our website~\cite{ourwebpage}.  This includes supporting
scripts\Comment{ (\eg, the scripts to run the tests and generate raw analysis
data)} and the full list of projects.

% SECTION 4

@@

\setlist[itemize]{leftmargin=1em}
\begin{itemize}
\item Feasibility
  \begin{itemize}
  \item \textbf{\numRQFeasibilityOne.} \RQFeasibilityOne
  \item \textbf{\numRQFeasibilityTwo.} \RQFeasibilityTwo    
  \end{itemize}
\item Adoption
  \begin{itemize}
  \item \textbf{\numRQAdoptionOne.} \RQAdoptionOne    
  \item \textbf{\numRQAdoptionTwo.} \RQAdoptionTwo
  \end{itemize}
\item Speedups
  \begin{itemize}
  \item \textbf{\numRQSpeedupOne.} \RQSpeedupOne
  \item \textbf{\numRQSpeedupTwo.} \RQSpeedupTwo
  \end{itemize}      
\item Tradeoffs
  \begin{itemize}
  \item \textbf{\numRQIssuesOne.} \RQIssuesOne    
  \end{itemize}
\end{itemize}

\subsection{Feasibility}
\label{sec:rqA}
\label{sec:rqB}

@@

% SECTION 5

@@

% SECTION 6
%%

@@

% SECTION 7
%%

@@

% SECTION 8
%%

@@

%\appendices
%\section{Proof of the First Zonklar Equation}
%Appendix one text goes here.

% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
%\section{}
%Appendix two text goes here.

% use section* for acknowledgment
%\ifCLASSOPTIONcompsoc
  % The Computer Society usually uses the plural form
%  \section*{Acknowledgments}
%\else
  % regular IEEE prefers the singular form
%  \section*{Acknowledgment}
%\fi

%The authors would like to thank...

@@

\balance
\bibliographystyle{plain}
\bibliography{tmp}

\begin{IEEEbiography}{Michael Shell}
Biography text here.
\end{IEEEbiography}

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{John Doe}
Biography text here.
\end{IEEEbiographynophoto}

% insert where needed to balance the two columns on the last page with
% biographies
%\newpage

\begin{IEEEbiographynophoto}{Jane Doe}
Biography text here.
\end{IEEEbiographynophoto}

% that's all folks
\end{document}

>>>>

\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{balance}
\usepackage{float}
\usepackage{url}
\usepackage{tabularx}
\usepackage[table]{xcolor}
\usepackage{booktabs}
\usepackage{subfigure} 
\usepackage{multirow}
\usepackage{mdframed}

\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  \usepackage[nocompress]{cite}
\else
  % normal IEEE
  \usepackage{cite}
\fi
\usepackage{amsmath}
\interdisplaylinepenalty=2500

\hyphenation{op-tical net-works semi-conduc-tor}

@@

@@

\title{Test Suite Parallelization in Open-Source Projects: A Study on Its Usage and Impact}

\author{Jeanderson~Candido,
        Luis~Melo,
        and~Marcelo~d'Amorim% <-this % stops a space
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem J. Candido, L. Melo, and M. d'Amorim
are affiliated to the Department of Computer Science, Federal University of
Pernambuco, Recife, PE, 50740-560 Brazil.\protect\\
% note need leading \protect in front of \\ to get a newline within \thanks as
% \\ is fragile and will error, could use \hfil\break instead.
E-mail: \{jbc5, lhsm, damorim\}@cin.ufpe.br}
\Comment{\thanks{Manuscript received \Fix{April 19, 2005}; revised \Fix{August 26, 2015}.}}}

@@

Considering a set of \numSubjs{} popular Java projects we analyzed, we
found that \percentMedLongRunning{} of the projects contain costly
test suites but parallelization features still seem underutilized in
practice~---~only \percentParallelUpdated{} of costly projects use
parallelization.  The main reported reason for adoption resistance was
the concern to deal with concurrency issues.  Results suggest that, on
average, developers prefer high predictability than high performance
in running tests.
\end{abstract}}

% make the title area
\maketitle

% To allow for easy dual compilation without having to reenter the
% abstract/keywords data, the \IEEEtitleabstractindextext text will
% not be used in maketitle, but will appear (i.e., to be "transported")
% here as \IEEEdisplaynontitleabstractindextext when the compsoc 
% or transmag modes are not selected <OR> if conference mode is selected 
% - because all conference papers position the abstract like regular
% papers do.
\IEEEdisplaynontitleabstractindextext
% \IEEEdisplaynontitleabstractindextext has no effect when using
% compsoc or transmag under a non-conference mode.

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\IEEEraisesectionheading{\section{Introduction}\label{sec:intro}}

Dealing with high testing costs has been an important problem in
software engineering research and industrial practice.  Several
approaches have been proposed in the research literature to address
this problem, with the focus mainly on test suite minimization,
prioritization, reduction, and selection~\cite{yoo-harman-stvr2012}.
In industry, the focus has been mainly on distributing the testing
workload.  Evidence of this are the Google TAP
system~\cite{google-tap,google-ci} and the Microsoft CloudBuild
system~\cite{prasad-shulte-ieee-microsoft-ci}, which provide
distributed infrastructures to efficiently build massive amounts of
code and run tests.  Building in-house server clusters is also a
popular mechanism to distribute testing workloads.  For example, as of
August 2013, the test suite of the Groupon PWA system, which powers
the \url{groupon.com} website, included over 19K tests.  To run all
those tests under 10m, Groupon used a cluster of 4 computers with 24
cores each~\cite{kim-etal-fse2013}.

At large organizations, the alternative of renting cloud
services~\cite{cloud-services} or even building proprietary
infrastructures for running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with modest
 or nonexistent budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  For these cases, the use of commodity
hardware\Comment{ (\eg{}, existing workstations)} is an attractive
solution for running tests.  The proliferation of
multi-core CPUs and the increasing popularization of testing
frameworks and build systems, which today provide mature support for
parallelization, enable\Comment{ test execution} speedups through increased CPU
usage~(see Section~\ref{sec:modes}).  These two elements~---~demand
for cost-effective test execution and supply of relatively inexpensive
testing infrastructures~---~inspired us to investigate 
test suite parallelization in practice.

This paper reports on an empirical study we conducted to analyze the
usage and impact of low-level parallelization to speed up testing in
open-source projects.  This is a relevant problem given the tremendous
popularity of open-source development and regression testing
research~\cite{yoo-harman-stvr2012}.  Note that parallelization is
complementary to other approaches to mitigate testing costs such as
(safe) test
selection~\cite{Rothermel:1997:SER:248233.248262,gligoric-etal-issta2015}
and continuous integration~\cite{Saff:2003:RWD:951952.952340}.

The dimensions of analysis we considered in this study are (i)
relevance, (ii) adoption, (iii) speedup, and (iv) tradeoffs.  The
dimension \emph{relevance} focuses on the potential of parallelization
to reduce testing costs. In the limit, parallelization would be
fruitless if all projects had short-running test suites, for example.  The
dimension \emph{adoption} evaluates how often existing open-source
projects use parallelization schemes and how developers involved in
costly projects (not using test suite parallelization) perceive this
technology.  It is important to measure resistance of practitioners to
the technology and to understand their reasons.  The dimension
\emph{speedup} evaluates the observed impact of
parallelization\Comment{~---~when used in selected open-source
  projects~---~} in running times.  Finally, the dimension
\emph{tradeoffs} evaluates the relationship between speedups obtained
with parallelization and issues that arise 
when running tests in parallel, including test
flakiness~\cite{luo-etal-fse2014,bell-etal-esecfse2015}.  We briefly summarize our findings
in the following.

\noindent\emph{Relevance.}~To assess how prevalent long-running test suites
are we selected \numSubjs{} popular Java projects from \github{} containing
Maven build files~\cite{maven}.  Section~\ref{sec:eval} details our methodology
to select subjects and to isolate our experiments from environmental noise.
Results indicate that nearly \percentMedLongRunning{} of the projects take at
least 1m to run and \percentLongRunning{} of the projects take at least 5m to
run.  Considering the \numMedLong{} projects with test suites taking longer than
a minute to run, the average execution time of a test suite was
\averageMedLongRunning{}.  Results also show that test cases are typically
short-running, typically taking less than half a second to run.  Furthermore, we
found that only in rare cases few test cases monopolize the overall time to run
a test suite.

\noindent\emph{Adoption.}~ We considered two aspects in measuring technology
adoption.  First, we measured usage of parallelism in open-source projects.
Then, we ran a survey with developers to understand the reasons that could
explain resistance to using the technology.\Comment{ For the quantitative
analysis we checked both statically (parsing build files) and dynamically
(monitoring execution of build files) for the presence of parallelization.}
Considering only the projects whose test suites take longer than a minute to
run, we found that only \percentParallelUpdated{} of them use parallelism.  We
also contacted developers from a selection of costly projects that did not use
parallelization to understand the reasons for not using parallelization.
Dealing with concurrency-related issues (\eg{}, the extra work to organize test
suite to avoid concurrency errors) and the availability of continuous
integration services were the most frequently answered reasons for not
considering parallelization.

\noindent\emph{Speedups.}~We used two setups to measure speedup.  In
one setup we selected projects that run test suites in parallel by
default, used a machine with eight virtual CPUs, and compared
execution times of test suites with and withouth (default) parallelism
enabled. In the other setup, we evaluated how execution scales with
the number of available cores in the machine. For that, we used a more
powerful machine with 80 virtual CPUs (40 cores with two native
threads on each core). Considering the first setup, results indicate
that the average speedup of parallelization was \avgSpeedup{}x.
Although we found cases with very high speedups (\eg{}, 28.8x for
project Jcabi), we also found cases where the speedups were not very
significant.  Considering the scalability experiment, we noticed,
perhaps as expected, that parallelization obtained with forking JVMs
scales with the number of cores but the speedup is bounded by
long-running test classes.

\noindent\emph{Tradeoffs.}~Test flakiness is a central concern when running
tests in parallel.  Dependent tests can be affected by different schedulings of
test methods and classes.  This dimension of the study measures the impact of
different parallel configurations on test flakiness and speedup.  Overall,
results indicate that configurations that fork JVMs do not achieve speedups as
high as other more-aggressive configurations, but they manifest much lower
flakiness ratios.

Our observations may trigger different actions:

%\setlist[itemize]{leftmargin=1.1em}
\begin{itemize}
\item \emph{Incentivize forking.}~Forked JVMs manifest very low rates
  of test flakiness.  Developers of projects with long-running test
  suites should consider using that feature, which is available in
  modern build systems today (\eg{}, Maven).
\item \emph{Break test dependencies.}~Non-forked JVMs can achieve
  impressive speedups at the expense of sometimes impressive rates of
  flakiness.  Breaking test dependencies (with
  ElectricTest~\cite{bell-etal-esecfse2015}, for example) to avoid flakiness is advised for developers with
  greater interest in efficiency.
\item \emph{Refactor tests for load balancing.}~The configuration with
  forked JVMs scales
  better\Comment{ with the number of cores} when the test workload is balanced
  across testing classes.  Automated refactoring could help balance
  the workload in scenarios where developers are not willing to change
  test code but have access to machines with a high number of cores.
\item \emph{Improve debugging for build systems.}~While preparing our
  experiments, we found scenarios\Comment{, related to test
    parallelization,} where Maven's executions did not reflect
  corresponding JUnit's executions.\Comment{(Docker reproduction scripts
  available.)} Those issues can hinder developers from using parallel
  testing. Better debugging support for build systems could help
  on that. 
\end{itemize}

The artifacts we produced as result of this study are available from
the following web page \webpage{}.

\section{Parallel Execution of Test Suites}
\label{sec:modes}

Figure~\ref{fig:levels} illustrates different levels where
parallelism in test execution can be obtained.
The highest level indicates
parallelism obtained through different machines on the
network.  For instance, using virtual machines from a cloud service to
\begin{wrapfigure}{r}{0.13\textwidth}  
  \vspace{-2mm}
  \centering
  %  \includegraphics[width=0.35\textwidth]{figs/parallel-levels.pdf}    
  \includegraphics[width=2cm]{figs/parallel-levels-short.pdf}  
  \caption{\label{fig:levels}Levels of parallelism.}
  \vspace{-2mm}
\end{wrapfigure}
distribute test execution.  The lowest levels denote parallelism
obtained within a single machine.  These levels are complementary:
the lowest levels leverage the computing power of server
nodes whereas the highest level leverages the aggregate processing
power of a network of machines.
This paper focuses on low-level parallelism, where computation can be
offloaded at different CPUs within a machine and at different threads
within each CPU.  This form of parallelism is enabled through build
systems (spawning processes in different CPUs) and testing frameworks
(spawning threads in one given CPU).  It is important to note that a variety
of testing frameworks provide today support for parallel test
execution (e.g., JUnit~\cite{junit-org}, TestNG~\cite{testng}, and
NUnit~\cite{nunit}) as to benefit from the available power of popular multi-core processors.
In the following, we elaborate relevant features of testing frameworks
and build systems for parallelization.  We focused on Java, Maven, and JUnit but the
discussion can be generalized to other language and tools.

@@

@@

We used \github{}'s search API~\cite{githubsearch} to identify
projects that satisfy the following criteria: (1) the primary language
is Java\footnote{In case of projects in multiple languages, the
  \github{} API considers the predominant language as the primary
  language.}, (2) the project has at least 100 stars, and (3) the latest
update was on or after \Jbc{January 1st, 2017}.
Although there is no clearcut limit on the number of \github{}
stars~\cite{github-stars} to define relevant projects, we observed that one
hundred stars was enough to eliminate trivial subjects.
The third criteria serves to skip projects without recent activity.
\Jbc{We focused on Java for its popularity.
It is important to highlight that the \github{}'s search API imposes a limit of
returning only the top 1000 results for a single query.
To overcome this limitation and have a larger sample set, we divided our
original query into multiple queries over subsequent periods of time and
considered the union the results.}
% Important to highlight that, as of now, the \github{}'s search API can only
% reflect contents from repository statistics (\eg, number of forks, main
% programming language); it does not provide a feature to search for projects
% containing certain files (\eg{}, \emph{pom.xml}) in the directory structure.
Figure~\ref{fig:subject-query} illustrates a query to the \github{} API as
an HTTP request.

\begin{figure}[t!]
\centering
\tiny
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    showstringspaces=false
}
\begin{lstlisting}
https://api.github.com/search/repositories?q=language:java
 +stars:>=100+pushed:2017-01-01..2017-02-01&page=1
\end{lstlisting}
  \vspace{-3mm}
  \caption{\label{fig:subject-query} Query to the \github{} API for projects
  that (1) use Java, (2) contains at least 100 stars, (3) has been updated
  between January 1st and February 1st of 2017.}
  \vspace{-5mm}
\end{figure}

We used the following methodology to select projects for analysis.
After obtaining the list of potential projects from GitHub, we filtered those
with Maven support (\ie, contains a \pomf{} file in the root directory).
We focused on Maven for its popularity in Java projects.
Then, considering this set of Maven projects, we executed the tests for
\SubjectsReruns{} times to discard those projects with issues in the build file
and non-deterministic results observed from sequential executions.

As of December 12th 2017, our search criteria returned a total of
\SubjectsGithub{} projects, and we identified \SubjectsMaven{} Maven projects.
\Fix{From this set of projects, \SubjectsGithubNotTestable{} projects were not
considered because of environment incompatibility (\eg, missing DBMS) and
\SubjectsGithubFlaky{} projects were discarded because of ``flaky
tests''~\cite{luo-etal-fse2014}.
A ``flaky'' test is a test that passes or fails under the same circumstances
leading to non-deterministic results.  As some of our experiments consist of
running tests on different threads, we ignored these projects as it would be
impractical to identify whether a test failed due to a race condition or some
other source of flakiness.
From the remaining \SubjectsGithubConsistant{} projects with deterministic
results, we eliminated \SubjectsGithubTooManyFailures{} projects with
\SuiteFailingThreshold{} or more failing tests as to reduce bias.
For the remaining projects with failing tests, we used the JUnit's
\CodeIn{@Ignore} annotation to ignore failing tests.
Our final set of subjects
contains \numSubjs{} projects.
Figure~\ref{fig:subjects} summarizes our sample set.}

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.27\textwidth]{results/piechart-subjs.pdf}
  \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
  hosted on \github{}. From this initial sample, we ignored
  \SubjectsGithubNotMaven{} projects without Maven support,
  \SubjectsGithubNotTestable{} with missing dependencies,
  \SubjectsGithubFlaky{} projects with flaky tests, and
  \SubjectsGithubTooManyFailures{} projects had at least
  \SuiteFailingThreshold{} of failing tests. We considered
  \numSubjs{} projects to conduct our study.}
\end{figure}

\label{sec:setup}
To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel processor
machine with eight virtual CPUs (four cores with two native threads each) and
16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr (64-bit version).
We used Java 8 and Maven 3.5.2 to build projects and run test suites.  To
process test results and generate plots we used Python, Bash, R and Ruby.
All source artifacts are publicly available for replication on our
website~\cite{ourwebpage}.
This includes supporting scripts and the full list of projects.

@@

\setlist[itemize]{leftmargin=1em}
\begin{itemize}
\item Relevance
  \begin{itemize}
  \item \textbf{\numRQFeasibilityOne.} \RQFeasibilityOne
  \item \textbf{\numRQFeasibilityTwo.} \RQFeasibilityTwo    
  \end{itemize}
\item Adoption
  \begin{itemize}
  \item \textbf{\numRQAdoptionOne.} \RQAdoptionOne    
  \item \textbf{\numRQAdoptionTwo.} \RQAdoptionTwo
  \end{itemize}
\item Speedups
  \begin{itemize}
  \item \textbf{\numRQSpeedupOne.} \RQSpeedupOne
  \item \textbf{\numRQSpeedupTwo.} \RQSpeedupTwo
  \end{itemize}      
\item Tradeoffs
  \begin{itemize}
  \item \textbf{\numRQIssuesOne.} \RQIssuesOne    
  \end{itemize}
\end{itemize}

\subsection{Relevance}
\label{sec:rqA}
\label{sec:rqB}

@@

@@

@@

@@

@@

%% \section*{Acknowledgements}
%% Jean(derson) and Luis are supported by FACEPE scholarphips
%% IBPG-0632-1.03/15 and IBPG-1175-1.03/16, respectively.  This work was
%% partially supported by CNPq grants 457756/2014-4 and 203981/2014-6.

@@

\balance
\bibliographystyle{IEEEtran}
\bibliography{tmp.bib}

\end{document}
